On Cybersecurity\\Science and Engineering\footnote{Confidential, restricted to the authors. Property of V-Research S.r.l.}

### 2020-05-25 reports/journal_paper/formal_glossary.tex
create report structure

A formalization requires a formal logic and a formal language.  We base our
formalization on first order logic (FOL) with the standard truth-value
semantics. The choice of this logic is usefull for the fomal treatment of the
theory we'll define in Section~\ref{sec:theory}.  We do not provide a proof
that the choice of FOL doesn't impede the formulation of a correct security
theory, nor that the semantics of English isn't an issue. So, we believe that
this doesn't pose an issue for the formulation of the seucirty hypotheses since
the hypothesis requires to be able to define \emph{an agent and its
honest/dishonest behaviors in such a way that an agent can be used to define a
system}. To the best of our knowledge, there is no result that shows that FOL
cannot be used to do so; on the contrary, using classical logic such as FOL or
Propositional logic is rather standard (along with Kripke structures for the
definition of the underlying causality principle).

@@

\subsection{Causality Principle}\label{sec:causality}
We formalize the Causality Principle starting from a K modal
logic\autocite{Garson2018modal} so that (i) we use a de-facto standard
way of defining the Causality Principle, and (ii) we do not restrict the causality
relation (between worlds) in any way (so we are as general and abstract as possible).
The standard definition of K modal logic is given in
Definition~\ref{def:modallogic} in terms of an interpretation function (which
we named $\sigma$ with a slight abuse of notation) defined in
Definition~\ref{def:modalinterpretation}. 
\begin{definition}{\bf K Modal Logic --}\label{def:modallogic}
A K-frame is a frame $ \kframe=\langle \possibleworlds,\modalrelation \rangle $
	in the K modal logic where $ \modalrelation $ is the binary relation
	(i.e. a set of ordered pairs) between possible worlds
	$\modalrelation\subseteq\possibleworlds\times\possibleworlds$, where
	$\possibleworlds$ represents the possible worlds, and
	$\possibleworlds\neq\emptyset$. An actual world
	$\actualworld\in\possibleworlds$ is assumed. For any proposition $P$,
	an interpretation function $\interpretation(\world,P)$ returns the
	truth value of $P$; e.g. $\interpretation(\world,P)=\top$ means that
	$P$ holds in $\world$. A model is defined as the tuple
	$\kmodel=\langle\possibleworlds,\modalrelation,\interpretation\rangle$.
\end{definition}

@@

As mentioned before, the accessibility relation $\modalrelation$ is free from
any axiomatic restriction (e.g. it's not reflexive nor anti-reflexive).  We
note that we have defined the Causality principle without considering it a
\emph{threat source} since, given that this is the first and outermost concept
in Figure~\ref{fig:safety-security}, we lack the concept of intent and
maliciousness (which are not inherent to the Causality Principle). 
In other words, the Causality principle or the Kripke structure
doesn't correlate cause-effect (or worlds) due to any other principle but
causality itself; therefore, in order to distinguish nominal or honest cause-effects
and non-nominal or dishonest ones we would need to add additional constraints, defining
what honesty is in a factious way.

Similarly, in the next sections we won't be able to discriminate between Nature
and Mankind due to their honesty. We argue that the concept of honesty, even if
we do not state that it is not intrinsic to all the definition of Nature or
Mankind, requires additional constraints or statements in order to be defined.
\fixnote{mr}{is connects with an equivalence? can it be correctly represented by $\subseteq$?}

@@

Mankind and Nature are considered as two abstract
agents, both defined as collections (i.e. an abstract type that does not imply a
specific implementation) of their sub-agents (i.e. humans for Mankind and
plants, animals, \&c.  for Nature). Similarly to\autocite{Santaca2016abf}, we
define Mankind and Nature, and any other agent in the reminder of this article,
as a meronomy (an hierarchy of Part-Whole relations) based on a standard
definition of mereology, i.e. based on the definition of Parthood relation
between \emph{Parts}.  Due to the necessity of considering different types of Part (as we'll show afterwards) we
extend the mereology to a
mereo-topology\autocite{Smith1996mereotopology,Varzi1994mereotopology,Rachavelpula2017mereotopology},
to increase the number of different types considered and to generalize the
relations between Parts (as in Table~\ref{tab:rcc358}).  For the sake of
readability, we use the term \emph{Region} both to refer to a mereological Part
and to a topological Region.  The choice of mereotopology is also correlated to
the objective of defining a formal ontology, which we use to define the
(formal) semantics of the terms (Parts) in Section~\ref{sec:problem}, and of
the concepts of safety and security (whole). We aim at creating a meronomy
instead of the taxonomies such as the one provided
in\autocite{NIST2020NVD,MITRE2020CVE} or instead of the poorly justified
CVSS\autocite{Mell2007CVSS} scoring system.

@@

In order to correlate the definition of
agent (i.e. Mankind and Nature) to the
mathematical structure of the logic that defines them, we express Mankind and
Nature as formulas over the theory of mereology and then in terms of
mereotopological Regions, extending the interpretation function
$\interpretation$, to include a formal theory of mereotopology.  We use the
Region Connection Calculus (RCC), as defined
in~\cite{bennettLogics,improvingRCC}, to provide an axiomatization of the
spatial concepts and relations in FOL to correlate the algebraic
structure to mereology. In its broader definition, the RCC theory is composed
by eight axioms, and is known as RCC8. In the text, for brevity, 
we will often focus only on RCC5 (without
loss of generality) by not considering tangential connections between spatial
Regions. We discuss the choice of RCC5 in more detail in
Section~\ref{sec:engsystemstate}. In Table~\ref{tab:rcc}, we
summarize the axioms of the Region Connection Calculus (see, e.g., \autocite{Grutter2008rcc}).

@@

\Paragraph{Attacker as a Dis-honest Agent}
As we mentioned in Section~\ref{sec:problem} when we postulated the
security hypothesis, Weaknesses and Vulnerability are the two core security
concepts of the current understanding of what security is. However, we see two
(opposed in terms of abstraction) possibility to better defined those concepts:
defining how an agent (Mankind or Nature) can maliciously use Weaknesses to
produce Vulnerability (and, in turn, Exploits), or how Errors can be defined
(since Error is a term from which Weakness are, in turn, defined).  The former,
in our current formalization, implies detailing and constraining the Causality
Principle by introducing constraints on how agents acts. For example,
introducing the concept of intentionality, motivation, or desire (see the BDI
framework defined in \autocite{Rao1995semantics} for a general overview of those concepts).
The symbolic approach (also called Dolev-Yao model) in the formal verification
of security and communication protocols, can be used in this spirit. The
attacker can be seen as an additional agent (often identified with the network
where the messages are exchanged) that sees the network traffic and manipulates
it. The actions are generic (the attacker can combine two messages, split a
message into its components, or decrypt/encrypt if it has the proper security
key) but not something that a dishonest agent cannot do. The main difference is
that an honest agent follows the nominal specification of the protocol while
the attacker doesn't. The attacker non-deterministically opens as many new
sessions as it wants and the causality structure in which this scenario
(protocol + attacker) has been defined, is searched for a state that is
considered erroneous with respect to some security requirements decided a
priori. Therefore, as we mentioned in Section~\ref{sec:problem}, the
formal verification of the security of protocols can be considered a scientific
security theory; the implementations resulting from the formalized (and
verified) design can be tested against the formalized security requirements.
So, it is not completely true that ``Thus, formal approaches offer no escape
from our basic problem; only by making unfalsifiable assumptions (about what an
attacker can do) will they allow derivation of a necessary condition'' (as
Herley describes in\autocite{Herley2009so}) rather, the
unfalsifiability-related issue seems to stem from how security conditions are
defined, i.e. how security requirements are defined. One can easily see that
this is not just an issue in the formal protocol verification community but the
very foundations of the concept of Weakness and Vulnerability are defined in a
way that makes it impossible (they are necessary conditions) to make a general
security statement on any system (even if we tested every single Weakness on
the CWE on our system it may be the case that a Weakness han yet to be
discovered). Therefore, we hypothesize that a security theory should define in
a complete way how errors (and then Weaknesses, Vulnerability, and Exploits)
may be introduced.

>>>>

A formalization requires a formal logic and a formal language.  We base our
formalization on first order logic (FOL) with the standard truth-value
semantics\footnote{The choice of this logic is usefull for the fomal treatment of the
theory we'll define in Section~\ref{sec:theory}.  We do not provide a proof
that the choice of FOL doesn't impede the formulation of a correct security
theory, nor that the semantics of English isn't an issue. So, we believe that
this doesn't pose an issue for the formulation of the security hypotheses.}.

@@

\subsection{Causality Principle}\label{sec:causality}
We formalize the Causality Principle starting from a K modal
logic\autocite{Garson2018modal} so that (i) we use a de-facto standard
way of defining the Causality Principle, and (ii) we do not restrict the causality
relation (between worlds) in any way (so we are as general and abstract as possible).
The standard definition of K modal logic is given in
Definition~\ref{def:modallogic} in terms of an interpretation function (which
we named $\sigma$ with a slight abuse of notation) defined in
Definition~\ref{def:modalinterpretation}. 
\begin{definition}{\bf K Modal Logic --}\label{def:modallogic}
A K-frame is a frame $ \kframe=\langle \possibleworlds,\modalrelation \rangle $
	in the K modal logic where $ \modalrelation $ is a binary relation
	(i.e. a set of ordered pairs) between possible worlds
	$\modalrelation\subseteq\possibleworlds\times\possibleworlds$, where
	$\possibleworlds$ represents the possible worlds, and
	$\possibleworlds\neq\emptyset$. An actual world
	$\actualworld\in\possibleworlds$ is assumed. For any proposition $P$,
	an interpretation function $\interpretation(\world,P)$ returns the
	truth value of $P$; e.g. $\interpretation(\world,P)=\top$ means that
	$P$ holds in $\world$. A model is defined as the tuple
	$\kmodel=\langle\possibleworlds,\modalrelation,\interpretation\rangle$.
\end{definition}

@@

As mentioned before, the accessibility relation $\modalrelation$ is free from
any axiomatic restriction (e.g. it's not reflexive nor anti-reflexive).  We
note that we have defined the Causality principle without considering it a
\emph{threat source} since, given that this is the first and outermost concept
in Figure~\ref{fig:safety-security}, we lack the concept of intent and
maliciousness (which are not inherent to the Causality Principle). 
In other words, the Causality principle or the Kripke structure
doesn't correlate cause-effect (or worlds) due to any other principle but
causality itself; therefore, in order to distinguish nominal or honest cause-effects
and non-nominal or dishonest ones we would need to add additional constraints, defining
what honesty is in a factious way.
Similarly, in the next sections we won't be able to discriminate between Nature
and Mankind due to their honesty. We argue that the concept of honesty, even if
we do not state that it is not intrinsic to all the definition of Nature or
Mankind, requires additional constraints or statements in order to be defined.
\fixnote{mr}{is connects with an equivalence? can it be correctly represented by $\subseteq$?}

@@

Mankind and Nature are considered as two abstract
agents, both defined as collections (i.e. an abstract type that does not imply a
specific implementation) of their sub-agents (i.e. humans for Mankind and
plants, animals, \&c.  for Nature). Similarly to\autocite{Santaca2016abf}, we
define Mankind and Nature, and any other agent in the reminder of this article,
as a meronomy (an hierarchy of Part-Whole relations) based on a standard
definition of mereology, i.e. based on the definition of Parthood relation
between \emph{Parts}.  Due to the necessity of considering different types of Part (as we'll show afterwards) we
extend the mereology to a
mereo-topology\autocite{Smith1996mereotopology,Varzi1994mereotopology,Rachavelpula2017mereotopology},
considering the relations in Table~\ref{tab:rcc358}.
For the sake of
readability, we use the term \emph{Region} both to refer to a mereological Part
and to a topological Region.  The choice of mereotopology is also correlated to
the objective of defining a formal ontology, which we use to define the
(formal) semantics of the terms (Parts) in Section~\ref{sec:problem}, and of
the concepts of safety and security (whole). We aim at creating a meronomy
instead of the taxonomies such as the one provided
in\autocite{NIST2020NVD,MITRE2020CVE} or instead of the poorly justified
CVSS\autocite{Mell2007CVSS} scoring system.

@@

In order to correlate the definition of
agents (i.e. Mankind and Nature) to the
mathematical structure of the logic that defines them, we express Mankind and
Nature as formulas over the theory of mereology and then in terms of
mereotopological Regions, extending the interpretation function
$\interpretation$ to include a formal theory of mereotopology.  We use the
Region Connection Calculus (RCC), as defined
in~\cite{bennettLogics,improvingRCC}, to provide an axiomatization of the
spatial concepts and relations in FOL to correlate the algebraic
structure to mereology. In its broader definition, the RCC theory is composed
by eight axioms, and is known as RCC8. In the text, for brevity, 
we will often focus only on RCC5 (without
loss of generality) by not considering tangential connections between spatial
Regions. We discuss the choice of RCC5 in more detail in
Section~\ref{sec:engsystemstate}. In Table~\ref{tab:rcc}, we
summarize the axioms of the Region Connection Calculus (see, e.g., \autocite{Grutter2008rcc}).

@@

\Paragraph{Attacker as a Dis-honest Agent}
As we mentioned in Section~\ref{sec:problem} when we postulated the
security hypothesis, Weaknesses and Vulnerability are the two core security
concepts of the current understanding of what security is. However, we see two
(opposed in terms of abstraction) possibility to better defined those concepts:
defining how an agent (Mankind or Nature) can maliciously use Weaknesses to
produce Vulnerability (and, in turn, Exploits), or how Errors can be defined
(since Error is a term from which Weakness are, in turn, defined).  The former,
in our current formalization, implies detailing and constraining the Causality
Principle by introducing constraints on how agents acts. For example,
introducing the concept of intentionality, motivation, or desire (see the BDI
framework defined in \autocite{Rao1995semantics} for a general overview of those concepts).
The symbolic approach (also called Dolev-Yao model) in the formal verification
of security and communication protocols, can be used in this spirit. The
attacker can be seen as an additional agent (often identified with the network
where the messages are exchanged) that sees the network traffic and manipulates
it. The actions are generic (the attacker can combine two messages, split a
message into its components, or decrypt/encrypt if it has the proper security
key) but not something that an honest agent cannot do. The main difference is
that an honest agent follows the nominal specification of the protocol while
the attacker doesn't. The attacker non-deterministically opens as many new
sessions as it wants and the causality structure in which this scenario
(protocol + attacker) has been defined, can be analyzed for a state that is
considered erroneous with respect to some security requirements decided a
priori. Therefore, as we mentioned in Section~\ref{sec:problem}, the
formal verification of the security of protocols can be considered a scientific
security theory; the implementations resulting from the formalized (and
verified) design can be tested against the formalized security requirements.
So, it is not completely true that ``Thus, formal approaches offer no escape
from our basic problem; only by making unfalsifiable assumptions (about what an
attacker can do) will they allow derivation of a necessary condition'' (as
Herley describes in\autocite{Herley2009so}) rather, the
unfalsifiability-related issue seems to stem from how security conditions are
defined, i.e. how security requirements are defined. One can easily see that
this is not just an issue in the formal protocol verification community but the
very foundations of the concept of Weakness and Vulnerability are defined in a
way that makes it impossible (they are necessary conditions) to make a general
security statement on any system (even if we tested every single Weakness on
the CWE on our system it may be the case that a Weakness han yet to be
discovered). Therefore, we hypothesize that a security theory should define in
a complete way how errors (and then Weaknesses, Vulnerability, and Exploits)
may be introduced.

### 2020-05-25 reports/journal_paper/problem_statement.tex
create report structure

in such approaches is not the definition of what cybersecurity is, but 
the generality of the results since they takle a specific step (and not the first) of the engineering process (of system).

@@

assumptions which non-evidently apply to a general security theory (since, as mentioned before,
there is no such a theory).

@@

		while a vulnerability should
		be defined in a way that is empirically falsifiable. This means
		that the term vulnerability should have a complete and sound

@@

Most of the safety-preserving principles in the field of engineering of
safety-critical cyber-physical systems (such as elevators and aircraft), upon
which safety requirements are defined (e.g. in standards such as the IEC 61508 or 61511\autocite{IEC201761511}), 
are based on empirical tests and measurements (therefore should be considered hypothesis and not definitions). While reasoning by
induction based on the empirical observation should be avoided, since it may
easily lead to false beliefs, this approach is
often justified by the supposed impossibility of defining a theory that
correctly predicts failures which, in turn, pose hazards to a system. 
To the best of our knowledge, and supported by\autocite{Herley2016unfalsifiability}, the
correlation between predictability of environment and believed unpredictability
of attackers has not been correlated to a theory on cybersecurity. 
Therefore, inductive research efforts in
predicting malicious effects are accepted (and published) in scientific
conferences (e.g.~\autocite{Rocchetto2014CSRF}). A failure of a wire due to
environment (e.g. due to humidity, dust, heat \&c) is defined from empirical
evidences and processes have been standardized to test qualities of hardware components.
This process completely breaks down when a malicious environment (i.e. an attacker)
is considered instead of the (supposedly honest and predictable)
natural environment. Therefore, the same approach that is in use for safety,
seems not to be applicable for security (e.g. for security testing).

@@

Either a valid security hypothesis can be formulated based on one or more of
the concepts reviewed (and depicted in Figure~\ref{fig:safety-security}) or it
can't.  Since, in the next Section, we will define our security hypothesis (on
top of which we'll deveop a security theory) on those terms, if the second case
is true we will not formulate a valid security theory. However, while we want
to highlight that the incompleteness of this review may be a potential issue;
on the other hand, due to the nature of a literature review, it seems to us
that only an inductive approach can be used and then any literature review will
be incomplete.  If the first case applies, in one of those terms one shall find
a valid ground on top of which formulate a security hypothesis (assuming that a
valid security hypothesis exists).

Our literature review shows that most of the definitions relates insecurity to
dis-honesty (also called maliciousness or adversarial) of an agent (often
called adversary or attacker).  If those correlation are important for the
insecurity of systems, it is plausible that they are important for the opposite
concept, security.  Therefore, we define the following hypothesis.
\begin{hypothesis}{\bf Security as Honesty and Insecurity as Dishonesty --}
	\begin{itemize}
		\item a closed system can be considered \emph{secure} if there
			is no dishonest agent
		\item a closed system can be considered \emph{insecure} if
			there is a dishonest agent 
	\end{itemize}
	where an agent is any virtual or physical entity of the system or using
	the system (e.g. a device, a software, or a human being) and dishonesty
	is not necessarily related to malicious motivation but also to
	incompetence or lack of skills.
\end{hypothesis}
As in the Dolev-Yao theory, we may correlate ``being dishonest'' to ``not
following the intended behavior/rules''.  In the case of a generic system, a
dishonest agent is therefore, any agent that doesn't follow the intended
behavior (or functionality or logic) of the system.  Given the generality of
the definition, and its high level of abstraction, we may
conclude that the hypothesis seems evident. For example, a software can be
considered an agent of the system and whenever it has a bug, it can be
exploited causing an Incident. However, this hypothesis has lead to the
un-testable conclusion that the dishonest behaviors of agents cannot be defined
in general (e.g. due to the heterogeneity of agents and systems) 
and that huge repository of dishonest behaviors should be kept as
definition, such as CWE\autocite{MITRE2020CWEresearch}, CVE\autocite{CVE},
CAPEC\autocite{MITRE2020CAPEC}, NVD\autocite{NIST2020NVD} and many many other;
or that dishonesty of an agent with respect to a security protocol should be
defined as a number of predefined actions as in
\autocite{Turuani2006clatse,Basin2005ofmc,Armando2016satmc,Rocchetto2017interpolation}
(to name a few).

>>>>

in such approaches is not the definition of what cybersecurity is but 
the generality of the results, since they takle a specific step (and not the first) of the engineering process (of system).

@@

assumptions which non-evidently apply to a general security theory.

@@

		%while a vulnerability should
		%be defined in a way that is empirically falsifiable. This means
		%that 
		On the other hand, the term vulnerability should have a complete and sound

@@

Most of the safety-preserving principles in the field of engineering of
safety-critical cyber-physical systems (such as elevators and aircraft), upon
which safety requirements are defined (e.g. in standards such as the IEC 61508 or 61511\autocite{IEC201761511}), 
are based on empirical tests and measurements (therefore should be considered hypothesis and not definitions). While reasoning by
induction based on the empirical observation should be avoided, since it may
easily lead to false beliefs, this approach is
often justified by the supposed impossibility of defining a theory that
correctly predicts failures.
%which, in turn, pose hazards to a system. 
To the best of our knowledge, and supported by\autocite{Herley2016unfalsifiability}, %the
there is no scientific theory that defines what a secure system is.
%correlation between predictability of environment and believed unpredictability
%of attackers has not been correlated to a theory on cybersecurity. 
Therefore, 
(inductive\footnote{``So, whenever they argue ``Every man is an
animal and Socrates is a man; therefore Socrates is an animal,'' proposing to
deduce from the universal proposition ``every man is an animal'' the particular
proposition ``Socrates therefore is an animal,'' which in fact goes (as we have
mentioned) to enstablish by way of induction the universal proposition, the
fall into the error of circular reasoning, since they are enstablishing the
universal proposition inductively by means of each of the particulars and
deducing the particular proposition from the universal syllogistically.''
Sextus Empiricus, Outlines of Pyrrhonism II-195
\autocite{Empiricus1990Pyrrhonism}})
research efforts in
predicting malicious effects are accepted (and published) in scientific
conferences (e.g.~\autocite{Rocchetto2014CSRF}). A failure of a wire due to
environment (e.g. due to humidity, dust, heat \&c) is defined from empirical
evidences and processes have been standardized to test qualities of hardware components.
This process completely breaks down when a malicious environment (i.e. an attacker)
is considered instead of the (supposedly honest and predictable)
natural environment. Therefore, the same approach that is in use for safety,
seems not to be applicable for security (e.g. for security testing).

@@

%Either a valid security hypothesis can be formulated based on one or more of
%the concepts reviewed (and depicted in Figure~\ref{fig:safety-security}) or it
%can't.  Since, in the next Section, we will define our security hypothesis (on
%top of which we'll develop a security theory) on those terms, if the second case
%is true we will not formulate a valid security theory. However, while we want
%to highlight that the incompleteness of this review may be a potential issue;
%on the other hand, due to the nature of a literature review, it seems to us
%that only an inductive approach can be used and then any literature review will
%be incomplete.  If the first case applies, in one of those terms one shall find
%a valid ground on top of which formulate a security hypothesis (assuming that a
%valid security hypothesis exists).

Our literature review shows that most of the definitions relates insecurity to
dis-honesty (also called maliciousness or adversarial) of an agent (often
called adversary or attacker). We can synthesize this belief in the
following hypothesis.

\begin{hypothesis}{\bf Security as Honesty and Insecurity as Dishonesty --}
	\begin{itemize}
		\item a closed system can be considered \emph{secure} if there
			is no dishonest agent
		\item a closed system can be considered \emph{insecure} if
			there is a dishonest agent 
	\end{itemize}
	where an agent is any virtual or physical entity of the system or using
	the system (e.g. a device, a software, or a human being) and dishonesty
	is not necessarily related to malicious motivation but also to
	incompetence or lack of skills.
\end{hypothesis}
As in the Dolev-Yao theory, we may correlate ``being dishonest'' to ``not
following the intended behavior/rules''.  In the case of a generic system, a
dishonest agent is, therefore, any agent that doesn't follow the intended
behavior (or functionality or logic) of the system.  Given the generality of
the definition, and its high level of abstraction, we may
conclude that the hypothesis seems evident. For example, a software can be
considered an agent of the system and whenever it has a bug, it can be
exploited causing an Incident. However, this hypothesis has lead to the
un-testable conclusion that the dishonest behaviors of agents cannot be defined
in general (e.g. due to the heterogeneity of agents and systems) 
and that huge repository of dishonest behaviors should be kept as
definition, such as CWE\autocite{MITRE2020CWEresearch}, CVE\autocite{CVE},
CAPEC\autocite{MITRE2020CAPEC}, NVD\autocite{NIST2020NVD};
or that dishonesty of an agent with respect to a security protocol should be
defined as a number of predefined actions as in
\autocite{Turuani2006clatse,Basin2005ofmc,Armando2016satmc,Rocchetto2017interpolation}
(to name a few).

### 2020-05-25 reports/journal_paper/tool.tex
create report structure

>>>>

\subsection{Impact and Likelihood}\label{sec:impact}
As described in~\autocite{CORASMethod}, in order to quantitatively estimate the
cybersecurity \emph{risk} of a CPS design, one needs to estimate both the
\emph{likelihood} of \emph{attack paths} (attack from now on)\fixnote{mr}{check terminology
consistency} along with their (negative) \emph{impact} on a requirement which, in
turn, is related to some \emph{company assets}. An attack that has a negative impact
on a requirement invalidates the requirement, leading to one or more \emph{incidents}.
